The Distributed Nature of Copycat..? (WIP)

### 2017-11-28 papers/paper.tex
Fixes typo
Adds additional notes and plans to paper

    Another important problem is defining the word "effective".
    I suppose that "effective" would mean capable of solving fluid analogy problems, producing similar answers to an identically biased human.
    However, it isn't clear to me that removing temperature increases the ability to solve problems effectively.
    Is this because models are aloud to have centralized structures, or because temperature isn't the only centralized structure?

@@

@@

\newline

>>>>

    Another important problem is defining the word "effective".
    I suppose that "effective" would mean capable of solving fluid analogy problems, producing similar answers to an identically biased human.
    However, it isn't clear to me that removing temperature increases the ability to solve problems effectively.
    Is this because models are allowed to have centralized structures, or because temperature isn't the only centralized structure?

@@

\subsubsection{Functional Programming Languages and the Brain}

    The original copycat was written in LISP, a mixed-paradigm language.
    Because of LISP's preference for functional code, global variables must be explicitly marked with surrounding asterisks.
    Temperature, the workspace, and final answers are all marked global variables as discussed in this paper.
    These aspects of copycat are all - by definition - impure, and therefore imperative code that relies on central state changes.
    It is clear that, since imperative, mutation-focused languages (like Python) are turing complete in the same way that functional, purity-focused languages (like Haskell) are turing complete, each method is clearly capable of modeling the human brain.
    However, the algorithm run by the brain is more similar to distributed, parallel functional code than it is to centralized, serial imperative code.
    While there is some centralization in the brain, and evidently some state changes, it is clear that 100\% centralized 100\% serial code is not a good model of the brain.

    Also, temperature is, ultimately, just a function of objects in the global workspace.
    The git branch soft-temp-removal hard-removes most usages of temperature, but continues to use a functional version of the temperature calculation for certain processes, like determining if the given answer is satisfactory or not.
    So, all mentions of temperature could theoretically be removed and replaced with a dynamic calculation of temperature instead.
    It is clear that in this case, this change is unnecessary.
    With the goal of creating a distributed model in mind, what actually bothers me more is the global nature of the workspace, coderack, and other singleton copycat structures.
    Really, when temperature is removed and replaced with some distributed metric, it is clear that the true "offending" global is the workspace/coderack.

    Alternatively, codelets could be equated to ants in an anthill (see anthill analogy in GEB).
    Instead of querying a global structure, codelets could query their neighbors, the same way that ants query their neighbors (rather than, say, relying on instructions from their queen).

@@
